Multiresolution Neural Field Estimation

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to model section

Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$. Therefore, we have
 w\left(r-r'\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
\label{eq:KernelFiniteExpansion}
 v_t\left(\mathbf{r}\right)\approx\boldsymbol\mu\left(\mathbf{r}\right)^\top\mathbf{x}_t

@@

where the unknown parameter $ \boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and the unknown state  $ \mathbf{x}_t \in \mathbb{R}^{n_x}$ are defined as 
 \boldsymbol\theta^\top=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
\label{KernelWeights}
 \mathbf{x}_{t}^\top=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right] 

@@

and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively. Similarly the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and  $\check{\mathbf{x}}_{t,j}$ contain all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ accordingly.
 The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu$ are defined by
 \boldsymbol\lambda^\top(\mathbf r-\mathbf r')=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right. \nonumber \\
&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
\label{KernelBasisVector} 

@@

 \boldsymbol\mu^\top(\mathbf r)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r) \cdots \boldsymbol\psi_{j}^\top(\mathbf r) \right] 
\label{FieldBasisVector}
Each vector of basis functions on the right hand-side of (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in a way similar to their corresponding weight vectors in (\ref{KernelWeights}) and (\ref{FieldWeights}). 
% Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales. In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.

>>>>

Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$. Therefore, the field and the connectivity kernel is approximated by
 w\left(r-r'\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right) 
\label{eq:KernelFiniteExpansion} \\
 v_t\left(r\right) &\approx \boldsymbol\mu\left(r\right)^\top\mathbf{x}_t,

@@

where the unknown parameter and state vectors \dean{(block matrices?)}, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
 \boldsymbol\theta^\top &=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
\label{KernelWeights} \\
 \mathbf{x}_{t}^\top &=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right].

@@

@@

The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively. Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.

The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu$ are defined by
\begin{align}
 \boldsymbol\lambda^\top(\mathbf r-\mathbf r')=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right. \nonumber \\
&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
\label{KernelBasisVector} 
\end{align}
\begin{equation}
 \boldsymbol\mu^\top(\mathbf r)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r) \cdots \boldsymbol\psi_{j}^\top(\mathbf r) \right] 
\label{FieldBasisVector}
\end{equation}
Each vector of basis functions on the right hand-side of (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in a way similar to their corresponding weight vectors in (\ref{KernelWeights}) and (\ref{FieldWeights}). 
% Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales. In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.
